---
title: "Web Scraping"
output:
  html_document:
    df_print: paged
---

## Introduction

We're going to try and scrape class schedules from the CSU website.
We'll start by using Dr. Buffardi's include function, because I'm just not certain that I have all the necessary libraries installed that I need, but this function will guarentee that I do.

```{r}
include <- function(library_name){
  if ( !(library_name %in% installed.packages()))
    install.packages((library_name))
  library(library_name, character.only = TRUE)
}
include("rvest")
include("tidyr")
```

## Setup
We're going to create variables of the different schedules we want to scrape for easy handling once we have created our webscraping function. We do this by creating a variable name (in our case we're just going to refer to them by their major and semester) and call `read_html()` on them.
```{r}

csciSpring2019 <-read_html("http://ems.csuchico.edu/APSS/schedule/spr2019/CSCI.shtml")

csciSpring2020 <-read_html("http://ems.csuchico.edu/APSS/schedule/spr2020/CSCI.shtml")


mathSpring2019 <-read_html("http://ems.csuchico.edu/APSS/schedule/spr2019/MATH.shtml")

mathSpring2020 <-read_html("http://ems.csuchico.edu/APSS/schedule/spr2020/MATH.shtml")

```


# Identifying sections
We can identify sections by inspecting the webpage with the webpage inspector. It will tell us what the types that we are looking for are.

```{r}
read_class_schedule <- function(url){

  table <- url %>% html_nodes("table")

  class_number <- table %>% 
                html_nodes("td.cat_num") %>% 
                html_text() %>%
                as.integer()
  
  section_number <- table %>% 
                html_nodes("td.sect") %>% 
                html_text() %>%
                as.integer()
  
  course_title <- table %>% 
                html_nodes("td.title") %>% 
                html_text() %>%
                as.character()

  instructor <- table %>% 
                html_nodes("td.Instructor") %>% 
                html_text() %>%
                as.character()

  enrollment <- table %>% 
                html_nodes("td.enrtot") %>% 
                html_text() %>%
                as.integer()

  schedule <- tibble(class= class_number, section= section_number, course = course_title, instructor= instructor, enrollment = enrollment)


return(schedule)
}
  
```



## Testing and Printing
We want call all our URLs from above and exhibit them each as a _tibble_.

```{r}
read_class_schedule(csciSpring2019)
read_class_schedule(mathSpring2019)
read_class_schedule(csciSpring2020)
read_class_schedule(mathSpring2020)
```

